To Be Decided

### 2025-07-17 paper/main.tex
More progress

            \noindent where $\text{FP}$ and $\text{FN}$ are the numbers of false-positive and false-negative pixels, respectively, and $\text{TP}$ is the total number of pixels that are part of the scatterers in the original image. Therefore, the indicator assumes values greater than or equal to zero. Note that values greater than 100\% are also possible, indicating that the reconstructed image has more incorrectly classified pixels than the total number of pixels that make up the scatterers in the original image. This can occur more frequently when the number of pixels of the scatterer in the original image is small.

@@

            It should be noted that inaccuracies in the reconstructed geometry of objects can significantly influence the position error calculation. For example, if a star-shaped object with five points is reconstructed with one point distorted, this distortion will affect the object's centroid, thereby impacting the position error. However, this effect is expected, as any criterion for determining an object's position inherently considers the pixels defining it, as it is for its geometry. Furthermore, the proposed indicator is straightforward and versatile, applicable even in scenarios involving images with multiple objects.

@@

                \begin{figure*}[!htb]
                    \centering
                    \subfigure[OSM, $\chi=0.25$]{\includegraphics[height=1.2in]{./experiments/vary/figs/osm_0.eps}}
                    \subfigure[OSM, $\chi=0.5$]{\includegraphics[height=1.2in]{./experiments/vary/figs/osm_1.eps}}
                    \subfigure[OSM, $\chi=0.75$]{\includegraphics[height=1.2in]{./experiments/vary/figs/osm_2.eps}}
                    \subfigure[OSM, $\chi=1$]{\includegraphics[height=1.2in]{./experiments/vary/figs/osm_3.eps}}
                    \subfigure[OSM, $\chi=1.5$]{\includegraphics[height=1.2in]{./experiments/vary/figs/osm_4.eps}} \\
                    \subfigure[SOM, $\chi=0.25$]{\includegraphics[height=1.in]{./experiments/vary/figs/som_0.eps}}
                    \subfigure[SOM, $\chi=0.5$]{\includegraphics[height=1.in]{./experiments/vary/figs/som_1.eps}}
                    \subfigure[SOM, $\chi=0.75$]{\includegraphics[height=1.in]{./experiments/vary/figs/som_2.eps}}
                    \subfigure[SOM, $\chi=1$]{\includegraphics[height=1.in]{./experiments/vary/figs/som_3.eps}}
                    \subfigure[SOM, $\chi=1.5$]{\includegraphics[height=1.in]{./experiments/vary/figs/som_4.eps}}
                    \caption{Shape recovering study, varying contrast: reconstructed images by OSM and SOM for different contrast values.}
                    \label{fig:shape:vary:recons}
                \end{figure*}

@@

                \begin{figure}[!htb]
                    \centering
                    \subfigure[]{\includegraphics[width=0.48\columnwidth]{./experiments/vary/figs/zeta_s.eps}\label{fig:shape:vary:indicators:zeta_s}} \hspace{0.01\columnwidth}
                    \subfigure[]{\includegraphics[width=0.48\columnwidth]{./experiments/vary/figs/dnl.eps}\label{fig:shape:vary:dnl}}
                    \caption{Shape recovering study, varying contrast: (a) shape error indicator $\zeta_S$ for OSM and SOM; (b) Degree of Nonlinearity (DNL) for each contrast value.}
                    \label{fig:shape:vary:indicators}
                \end{figure}

@@

>>>>

            \noindent where $\text{FP}$ and $\text{FN}$ are the numbers of false-positive and false-negative pixels, respectively, and $\text{TP}$ is the total number of pixels that are part of the scatterers in the original image. Therefore, the indicator assumes values greater than or equal to zero. Note that values greater than 100\% are also possible, indicating that the reconstructed image has more incorrectly classified pixels than the total number of pixels that make up the scatterers in the original image. This can occur more frequently when the number of pixels of the scatterer in the original image is small. The Algorithm \ref{alg:compute_zeta_s} summarizes the steps for calculating the shape error indicator.

            \input{algorithms/zetas.tex}

@@

            It should be noted that inaccuracies in the reconstructed geometry of objects can significantly influence the position error calculation. For example, if a star-shaped object with five points is reconstructed with one point distorted, this distortion will affect the object's centroid, thereby impacting the position error. However, this effect is expected, as any criterion for determining an object's position inherently considers the pixels defining it, as it is for its geometry. Furthermore, the proposed indicator is straightforward and versatile, applicable even in scenarios involving images with multiple objects. The Algorithm \ref{alg:compute_zeta_p} summarizes the steps for calculating the position error indicator.

            \input{algorithms/zetap.tex}

@@

                \begin{figure*}[!htb]
                    \centering
                    \subfigure[OSM, $\chi=0.25$]{\includegraphics[height=1.2in]{../experiments/vary/figs/osm_0.eps}}
                    \subfigure[OSM, $\chi=0.5$]{\includegraphics[height=1.2in]{../experiments/vary/figs/osm_1.eps}}
                    \subfigure[OSM, $\chi=0.75$]{\includegraphics[height=1.2in]{../experiments/vary/figs/osm_2.eps}}
                    \subfigure[OSM, $\chi=1$]{\includegraphics[height=1.2in]{../experiments/vary/figs/osm_3.eps}}
                    \subfigure[OSM, $\chi=1.5$]{\includegraphics[height=1.2in]{../experiments/vary/figs/osm_4.eps}} \\
                    \subfigure[SOM, $\chi=0.25$]{\includegraphics[height=1.in]{../experiments/vary/figs/som_0.eps}}
                    \subfigure[SOM, $\chi=0.5$]{\includegraphics[height=1.in]{../experiments/vary/figs/som_1.eps}}
                    \subfigure[SOM, $\chi=0.75$]{\includegraphics[height=1.in]{../experiments/vary/figs/som_2.eps}}
                    \subfigure[SOM, $\chi=1$]{\includegraphics[height=1.in]{../experiments/vary/figs/som_3.eps}}
                    \subfigure[SOM, $\chi=1.5$]{\includegraphics[height=1.in]{../experiments/vary/figs/som_4.eps}}
                    \caption{Shape recovering study, varying contrast: reconstructed images by OSM and SOM for different contrast values.}
                    \label{fig:shape:vary:recons}
                \end{figure*}

@@

                \begin{figure}[!htb]
                    \centering
                    \subfigure[]{\includegraphics[width=0.48\columnwidth]{../experiments/vary/figs/zeta_s.eps}\label{fig:shape:vary:indicators:zeta_s}} \hspace{0.01\columnwidth}
                    \subfigure[]{\includegraphics[width=0.48\columnwidth]{../experiments/vary/figs/dnl.eps}\label{fig:shape:vary:dnl}}
                    \caption{Shape recovering study, varying contrast: (a) shape error indicator $\zeta_S$ for OSM and SOM; (b) Degree of Nonlinearity (DNL) for each contrast value.}
                    \label{fig:shape:vary:indicators}
                \end{figure}

@@

        \subsection{Breast Phantom Study}\label{sec:results:breast}
